---
title: "Litter sizes vs number of litters"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
    code_folding: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width = 8, collapse = TRUE)
```

```{r, include=FALSE, warning=FALSE, }
install.packages("tidyverse", repos = "http://cran.us.r-project.org")
library(tidyverse)
library(dplyr)
install.packages("ggsignif", repos = "http://cran.us.r-project.org")
library(ggsignif)
install.packages('ggpubr', repos = "http://cran.us.r-project.org")
library(ggpubr)
install.packages('rstatix', repos = "http://cran.us.r-project.org")
library(rstatix)

ls<-read.csv("/Users/charris/Desktop/F5miceTest/litter_sizes_tidy.csv")
# Add a numeric generation column for plotting
ls <- ls %>%
  mutate(generation_num = case_when(
    generation_parent == "P" ~ 0,
    generation_parent == "F1" ~ 1,
    generation_parent == "F2" ~ 2,
    generation_parent == "F3" ~ 3,
    generation_parent == "F4" ~ 4,
  ))
```

# Litter size for each generation

Number of pups for all litter numbers

```{r}

# Graph the litter sizes over the generations

ls %>%
  filter(genotype != "Fancm+/-") %>%
  filter(generation_num != 0) %>%
  ggplot(aes(x = generation_num, y = pup_number, colour = genotype)) +
  geom_jitter(width = 0.1) +
  geom_smooth(method = "lm") +
  scale_x_discrete(limits=c("F1", "F2", "F3", "F4"))+
  xlab("Parent generation") + ylab("Number of pups")
```

# Compare the litter size with litter number

The number of pups per litter decreases with litter number in both genotypes

```{r}
ls %>%
  filter(genotype != "Fancm+/-") %>%
  #filter(genotype != "Fancm-/-") %>%
  filter(generation_num != 0) %>%
  ggplot(aes(x = generation_num, y = litter_number, colour = genotype)) +
  geom_jitter(width = 0.1) +
  geom_smooth(method = "lm") +
  #scale_x_discrete(limits=c("F1", "F2", "F3", "F4"))+
  xlab("Litter number") +  ylab("Number of pups")
```

Compare the litter sizes for only the 1st litters

```{r}
ls %>%
  filter(genotype != "Fancm+/-") %>%
  #filter(genotype != "Fancm-/-") %>%
  filter(generation_num != 0) %>%
  filter(litter_number == 1) %>%
  ggplot(aes(x = generation_num, y = pup_number, colour = genotype)) +
  geom_jitter(width = 0.1) +
  geom_smooth(method = "lm") +
  scale_x_discrete(limits=c("F1", "F2", "F3", "F4"))+
  xlab("Parent generation") + ylab("Number of pups") +
  ggtitle("Litter sizes from 1st litters")
```

Compare the litter sizes for only the 2nd litters

```{r}
ls %>%
  filter(genotype != "Fancm+/-") %>%
  #filter(genotype != "Fancm-/-") %>%
  filter(generation_num != 0) %>%
  filter(litter_number == 2) %>%
  ggplot(aes(x = generation_num, y = pup_number, colour = genotype)) +
  geom_jitter(width = 0.1) +
  geom_smooth(method = "lm") +
  scale_x_discrete(limits=c("F1", "F2", "F3", "F4"))+
  xlab("Parent generation") + ylab("Litter size")+
  ggtitle("Litter sizes from 2nd litters")
```

Compare the litter sizes for only the 3rd litters

```{r}
ls %>%
  filter(genotype != "Fancm+/-") %>%
  #filter(genotype != "Fancm-/-") %>%
  filter(generation_num != 0) %>%
  filter(litter_number == 3) %>%
  ggplot(aes(x = generation_num, y = pup_number, colour = genotype)) +
  geom_jitter(width = 0.1) +
  geom_smooth(method = "lm") +
  scale_x_discrete(limits=c("F1", "F2", "F3", "F4"))+
  xlab("Parent generation") + ylab("Number of pups")+
  ggtitle("Litter sizes from 3rd litters")
```

Compare the litter sizes for only the 4th litters

```{r}
ls %>%
  filter(genotype != "Fancm+/-") %>%
  #filter(genotype != "Fancm-/-") %>%
  filter(generation_num != 0) %>%
  filter(litter_number == 4) %>%
  ggplot(aes(x = generation_num, y = pup_number, colour = genotype)) +
  geom_jitter(width = 0.1) +
  geom_smooth(method = "lm") +
  scale_x_discrete(limits=c("F1", "F2", "F3", "F4"))+
  xlab("Parent generation") + ylab("Number of pups")+
  ggtitle("Litter sizes from 4th litters")
```